Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-11-30 docs/appendixB.Rmd
updates appendices

Spatial dependence existed in the residuals until pixels were separated by about 500 meters (Fig. B1). Thus, we set the kernal bandwidth ($\sigma$ in Eq. X of the main text) to 500/3 = `r round(500/3,2)`. We then placed equally-spaced knots across our spatial grid until the distance between nearest neighbors was approximately 500 meters. Knots were placed evenly across space in the x and y directions. This resulted in a 10 $\times$ 20 knot grid (200 knots; Fig. B2).

![Spatial variogram of model residuals showing where spatial dependence disappears (~500 meters; asymptote of the variogram), and the value chosen for the kernal bandwidth in Eq. 6 of the main text (500/3; dashed black line).](components/avgresidual_variogram_withrange_subset.png)

![Map of our study area showing percent cover in 1984 and the location of the 200 evenly-spaced knots.](components/SAGE_Grid_wKnots_subset.png)

>>>>

Spatial dependence existed in the residuals until pixels were separated by about 500 meters (Fig. B1). Thus, we set the kernal bandwidth ($\sigma$ in Eq. X of the main text) to 500/3 = `r round(500/3,2)`. We then placed equally-spaced knots across our spatial grid until the distance between nearest neighbors was approximately 500 meters. Knots were placed evenly across space in the x and y directions. This resulted in a 11 $\times$ 21 knot grid (231 knots; Fig. B2).

![Spatial variogram of model residuals showing where spatial dependence disappears (~500 meters; asymptote of the variogram), and the value chosen for the kernal bandwidth in Eq. 6 of the main text (500/3; dashed black line).](../results/avgresidual_variogram_withrange_subset.png)

![Map of our study area showing percent cover in 1984 and the location of the 231 evenly-spaced knots.](../results/SAGE_Grid_wKnots_subset.png)

### 2015-11-30 docs/appendixD.Rmd
updates appendices

```{r figure_D1,dependson="plot-options", fig.cap="Standardized percent cover showing the general spatial structure of above and below average pixels in the data (top panel) compared to the mean posterior estimate of the spatial field, $\\eta$ (bottom panel).", eval=TRUE, echo=FALSE}
library(png)
library(grid)
img <- readPNG("./components/spatialfield.png")
grid.raster(img)
```

>>>>

```{r figure_D1,dependson="plot-options", fig.cap="Standardized percent cover showing the general spatial structure of above and below average pixels in the data (top panel) compared to the mean posterior estimate of the spatial field, $\\eta$ (bottom panel).", eval=TRUE, echo=FALSE}
library(png)
library(grid)
img <- readPNG("../results/spatialfield.png")
grid.raster(img)
```
